---
title: "PredMachLearn1"
author: "Arnaud Lagarde"
date: "Saturday, February 21, 2015"
output: html_document
---
```{r,warning=FALSE,echo=FALSE}
library(caret)
library(randomForest)
```

Getting Data
------------
Let's load and have a look at the data first

```{r}
Rawtraining<-read.csv("pml-training.csv")
Rawtesting<-read.csv("pml-testing.csv")
```

Cleaning Data
-------------
First we will remove all the columns which contains a majority of blanks and  NAs.
Then we remove the first seven columns which contains irrelevant datas (user name, time stamp, etc...)
Then we use the nearZeroVar function on remaining columns to check we got only potentially useful predictors. 

```{r}
colmarker<-c(1:dim(Rawtraining)[2])
badcol<-which(sapply(colmarker,function(x){sum(is.na(Rawtraining[,x])|Rawtraining[,x]=="")})>19000)
training<-Rawtraining[,-c(1:7,badcol)]
testing<-Rawtesting[,-c(1:7,badcol)]
NearZero<-nzv(training,saveMetrics=TRUE)
which(NearZero$nzv)
```

Now, we divide the training set, into two datasets, one with 70% of the data to train the model, the remaining one to test it (Mtrain and Mtest)

```{r}
set.seed(1255)
inTrain <- createDataPartition(y=training$classe, p=0.7, list=FALSE)
Mtrain<-training[inTrain,]
Mtest<-training[-inTrain,]

```

Model fitting
-------------
We will try to fit a random forest model, using Mtrain.
Then we use this model to predict the Mtest classe, and check the accuracy with the confusion matrix.


```{r}
fit<-randomForest(classe~.,data=Mtrain)
pred<-predict(fit, Mtest, type = "class")
confusionMatrix(pred, Mtest$classe)
```

Conclusion
----------
That's a really high accuracy, above 99%. 
We use random forest so there is no need for cross-validation or a separate test set to get an unbiased estimate of the test set error, as it is estimated internally. The expected out of sample error is 0.66%. 
With this kind of accuracy, we don't expect any misclassification on our test samples of just 20 datas. Let's do the prediction for the test data.

```{r}
answers<-predict(fit, testing, type="class")
pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}
pml_write_files(answers)

```